Implicit neural representation of potential fields

### 2024-06-06 authorship_declaration.tex
Address reviewer 2's annotated thesis
Add header and chapter numbers to sections
De-number authorship declaration because including signed pdf copy, fixes TOC page length
Drop line from declaration per EJ email

\documentclass[manuscript.tex]{subfiles}
\begin{document}

\addsec{Authorship Declaration}
This research was carried out at the University of Western Australia.
This thesis contains material that has been published or prepared for publication.
The extent of the candidate's contribution toward publication is outlined below.

@@

\noindent{}The possible application of super-resolution for geophysical grid data was suggested by E.J. Holden.

\medskip{}
\noindent{}Sections comprising published journal articles:
\begin{itemize}
      \item{}\textbf{Location in thesis}: Chapter 1

            \textbf{Publication}: Smith, L., Horrocks, T., Holden, E.J., Wedge, D., Akhtar, N., 2022. Magnetic grid resolution enhancement using machine learning: A case study from the Eastern Goldfields Superterrane. Ore Geology Reviews 150, 105119. https://doi.org/10.1016/j.oregeorev.2022.105119

@@

\noindent{}Sections comprising manuscripts in preparation:
\begin{itemize}
      \item{}
            \textbf{Location in thesis}: Chapter 2

@@

      \item{}
            \textbf{Location in thesis}: Chapter 3

>>>>

% \documentclass[manuscript.tex]{subfiles}
% \begin{document}

\addsec*{Authorship Declaration}
This research was carried out at the University of Western Australia.
This thesis contains material that has been published or prepared for publication.
The extent of the candidate's contribution toward publication is outlined below.

@@

% \noindent{}The possible application of super-resolution for geophysical grid data was suggested by E.J. Holden.

\medskip{}
\noindent{}Sections comprising published journal articles:
\begin{itemize}
      \item{}\textbf{Location in thesis}: Chapter 2

            \textbf{Publication}: Smith, L., Horrocks, T., Holden, E.J., Wedge, D., Akhtar, N., 2022. Magnetic grid resolution enhancement using machine learning: A case study from the Eastern Goldfields Superterrane. Ore Geology Reviews 150, 105119.
            \url{https://doi.org/10.1016/j.oregeorev.2022.105119}

@@

\noindent{}Sections comprising manuscripts in preparation:
\begin{itemize}
      \item{}
            \textbf{Location in thesis}: Chapter 3

@@

      \item{}
            \textbf{Location in thesis}: Chapter 4
